---
title: "Week 12 documentation"
author: "Pan Chen"
date: "1/19/2018"
output: html_document
---
## Where are the tables?
The two tables (disambReference,disambintlpatref) with 'coauthor' columns are in "week 12 Data.RData", the reason they are not exported or pushed to our MySQL server is because 'coauthor' column is a dataframe which resides in a dataframe to make the coauthor matching function work, so they are not "exportable" flat 2-D tables.

What we have in MySQL server now is the test.disambReference,test.disamb_IntlPatentReference tables in the disambiguation format without the coauthor columns

To generate the coauthor column from test.disambReference,test.disamb_IntlPatentReference tables, please follow the R code [**here**](https://github.com/cpkoywk/Genbank/blob/master/Week%2010%20-%20Generating%20Coauthor%20Column.R)

## What do we have at the end of the Fall 2017 Semester
Assume we have loaded week 12 Data.RData from rstudio10
```{r}
#please kindly unquote these...
# tmp1<-head(disambReference,1000)
# tmp2<-head(disambintlpatref,1000)
```
Their "coauthor" column is another dataset, so each of these dataframe has a dataframe within it
Flatten them so they could be exported to csv.
```{r}
#unquote these...
#tmp1$coauthor<-sapply(tmp1$coauthor, FUN = function(x) paste(x,collapse = ', ',sep=''))
#tmp2$coauthor<-sapply(tmp2$coauthor, FUN = function(x) paste(x,collapse = ', ',sep=''))
#write.csv(tmp1,file = 'data/disambReference_sample.csv')
#write.csv(tmp2,file = 'data/disambIntlpatref_sample.csv')
```
Now let's work primarily with our exported sample datasets
```{r}
disambReference<-read.csv('data/disambReference_sample.csv',row.names = 1)
disambIntlpatref<-read.csv('data/disambIntlpatref_sample.csv',row.names = 1)
head(disambReference)
head(disambIntlpatref)
```
Here's the code for the co-author matching function between disambReference and disambIntlpatref tables:
```{r}
f <- function(x) {
b<-sapply(X = x[[8]], FUN = function (X) { grep(X, x[[15]], ignore.case = TRUE, fixed = TRUE, perl=FALSE) }, simplify = "array")
  return (length(unlist(b)))
}
```
Here's an example on how to use this function: the reason it doesn't work with our sample dataset is probably because I have flattened the coauthor columns of both tables...

if it works correctly, match1 would be a table whose rows represent all of the patents and references with the matching Author FName and LName

nummatch column represents the number of the coauthor matches between the (FName, LName) matching reference and patent.

```{r}
#match<-merge(disambReference, disambIntlpatref, by.x = c("Fname","Lname"), by.y = c("Fname","Lname"), all.x = FALSE, all.y = FALSE)
#match$nummatch<-apply(match1, 1, f)
```
TODO:
However, what we got stuck at the end of the last semester (Fall 2017) is, this method did not seem to be able to disambiguate the following scenario:

Assume we have a Reference Table, which has three records

R1. Sarah, Pan  
R2. Sarah, Jeff  
R3. Sarah, Pan, Jeff  

Assume we have a Patent Table, which has 1 record  
P1. Pan, Jeff  

From this method, it looks like Pan from R1 and Pan from P1 are the same Pan, and Jeff from R2 and Jeff from P1 are the same Jeff, because they both worked with a "Sarah", but with the current workflow, they would not be disambiguated. Only R3's Pan and Jeff would be disambiguated.

I think this could be a starting point of one of the things to work on for the future.

And the parsed tables (disambReference, disambIntlpatref) can be found in week 12 Data.RData in RStudio10. 
