---
title: "Week1: Parsing Cleaning Transforming ReferencePatent table"
output:
  pdf_document: default
  html_notebook: default
---

```{r}
#Load Necessary packages
library(reshape2)
library(plyr)
library(dbConnect)
#library(ggplot2)
#library(ggmap)
library(lubridate)
library('splitstackshape')

```
# Parsing Cleaning Transforming ReferencePatent table
## Objective:
We are trying to parse the original ReferencePatent table into a final output table, which contains the following attributes: id, authors (original field), title, patentType (e.g. EP, US, GB), PatentNumber (e.g. 0238993), version (e.g. -A2 1), patentDay, PatentMonth, PatentYear, extra_journal (the leftover data that comes after the semi-colon or that is  not any of the previously indicated patent data), and then the parsed author names (one per column (e.g. Author 1, Author 2, Author 3). 

### Get the Reference Patent table from the SQL server
```{r}
#uncomment next line for the real thing
#ReferencePatent<-dbGetQuery(con,'select * from genbank.ReferencePatent')
ReferencePatent<-read.csv('data/ReferencePatent1000.csv',row.names=1)
```
### Parse Author Column:
```{r}
#Split Author names of the real set
paste("the original column:")
head(ReferencePatent$authors,10)
#eliminate "\t"
authorsplit<-gsub("\t", " ", ReferencePatent$authors, fixed=TRUE)
#head(authorsplit)
#eliminate "and"
authorsplit<-gsub(" and ", ", ", authorsplit, fixed=TRUE)
#head(authorsplit)
#split it by ", " because two author names are split by ", "
authorsplit<-strsplit(authorsplit,", ")
#the number of authors the patent with most authors has
paste("the number of authors the patent with most authors has:", max(unlist(lapply(authorsplit, function(x) length(x)))))
    
#The result
paste("the parsed column:")
head(authorsplit)
```
### Transpose the Author column:
For an author cell like 

| Author                            |   |
|-----------------------------------|---|
| 'Kozlov,J.I.' 'Naroditskaya,V.A.' |   |

we want to separate it into two separate cells

| Author                            | Author1     | Author2             |
|-----------------------------------|-------------|---------------------|
| 'Kozlov,J.I.' 'Naroditskaya,V.A.' | Kozlov,J.I. | 'Naroditskaya,V.A.' |
```{r}
#Create a new dataframe for this task:
pat<-as.data.frame(ReferencePatent$authors)
#Write a for loop to populate the tranposed author columns
for (i in 1:max(unlist(lapply(authorsplit, function(x) length(x))))){
  eval(parse(text = paste0('pat$Author', i, ' <- sapply(authorsplit,function(x) x[i])')))
}

head(pat)
```
### Parse content out of the journal column:
```{r}
#1. parse patentType out of journal column
head(ReferencePatent$journal,10)
#sub "\t" and split the journal column by ' '
journal<-strsplit(gsub("\t", " ", ReferencePatent$journal, fixed=TRUE)," ")
head(journal,10)
#the second part of each row of 'journal' list is the patenttype that we need
pat$patentType<-sapply(journal,function(x) x[2])
head(pat$patentType,10)
#2. parse patent number out of journal column
head(journal)
patentNumber<-strsplit(sapply(journal,function(x) x[3]), "-")
pat$patentNumber<-sapply(patentNumber,function(x) x[[1]])
head(pat$patentNumber)
#3. parse patentVersion (something like -A2 1) out of journal column
head(journal)
version1<-sapply(patentNumber,function(x) x[2])
head(version1)
version2<-sapply(journal,function(x) x[4])
head(version2)
#mapply is kind of like zip in python
version3<-mapply(c, version1, version2, SIMPLIFY=FALSE)
#head(version3)
pat$patentVersion<-as.vector(sapply(version3,function(x) paste(x[1],x[2])))
head(pat$patentVersion)
#4. patentDay, patentmonth, patent year (requires 'lubridate')
head(journal)
fulldate<-dmy(sapply(journal,function(x) x[5]))
pat$patentYear<-year(fulldate)
pat$patentMonth<-month(fulldate)
pat$patentDay<-day(fulldate)
#5. split the journal column on the first occrence of ";\t" to get extra portion of the journal
patentExtra<-as.vector(colsplit(ReferencePatent$journal,";\t",c("a","b"))[2])
pat$patentExtra<-patentExtra$b
head(pat$patentExtra)
#Final Results
head(pat)
```
We are only going to need the 

# 2. Transforming Reference Table:
Parse the genbank.reference table in the same way I did the ReferencePatent Table: keep the id, title, journal, authororginal, author1,2,3,4,pubmed,year,reference

```{r}
Reference<-dbGetQuery(con,'select * from genbank.Reference')
colnames(Reference)
colnames(parsedReference)
parsedReference<-as.data.frame(Reference$id)
parsedReference$title<-Reference$title
parsedReference$reference<-Reference$reference
parsedReference$origauthors<-Reference$authors
parsedReference$consortium<-Reference$consortium
parsedReference$journal<-Reference$journal
parsedReference$pubmed<-Reference$pubmed
parsedReference$remark<-Reference$remark
parsedReference$year<-Reference$year
parsedReference$new_id<-Reference$new_id

'''